ESRC SDAI Application - Understanding domestic abuse using Big Data

### 2019-07-23 pathways_to_impact.tex
Pathways tinkering

We will work with West Midlands Police to import the insight from the research into their day-to-day processes and also to their senior managment team: 1. The programme on ``predictors of serious harm'' into the THRIVE+ (threat, harm, risk, investigation, vulnerability, engagement, pervention and intervention) risk assessment model used for assessing calls and reports of domestic abuse. 2. The programme on the  ``decision to report'' can link with police's design of the inital contact with victims (e.g., https://west-midlands.police.uk/your-options/domestic-abuse) and ``police mis-recording of abuse'', which is of direct interest to their data quality and reporting. 3. The programme on ``envionmental factors influencing abuse'' can be used to help predict which local populations are most at risk of abuse in the West Midlands,

@@

Within Lloyds Bank, we will work with Martin King, Head of Customer Vulnerability. Warwick already has a relation with King's team in CI Stewart's work on the effects of gambling, which was completed using micro-level transaction data from millions of account holders. Key issues here are work on coercion and control, and having sufficient financial resiliance to escape an abusive relationship. Our day-to-day contact at Lloyds is Dr David Leake, Head of the Behavioural Insights Team. We will present the findings from all four programmes to the Lloyds Vulnerability Team in six-monthly briefings, and work to integrate insight from the research into the Lloyds environment.

@@

Impact summit (1 day at the Shard)
Visits to key charities
Visits to West Midlands Police
Presentation to NPCC
Data sprint session with WMP Behavioural Insights Team?

@@

PI Mullett will spend half of his time of the project leading the impact activity and takes overall responsibility of delivering the impact programme. Mullett has worked extensively on the impact programme from the ESRC funded ``Accumulating to Choose'' programme, with the Financial Conduct Authority. CI Stewart will also spend half of his time of the project on the impact activity. Stewart has significant experience of impact acitivites in the domain of financial decision making with Lloyds Banking Group, Barclays Bank, and the UK Finance Association. Postdoc Trendl will be fully involved in the impact programme, and this is also an important part of the professional development for an early career researcher, and will allow her to establish a network of independent contacts. Trendl will spend one third of her time on the programme on the impact activities.

>>>>

We will work with West Midlands Police to import the insight from the research into their day-to-day processes and also to their senior management team: 1. The programme on ``predictors of serious harm'' into the THRIVE+ (threat, harm, risk, investigation, vulnerability, engagement, pervention and intervention) risk assessment model used for assessing calls and reports of domestic abuse. 2. The programme on the  ``decision to report'' links with police's design of the inital contact with victims (e.g., https://west-midlands.police.uk/your-options/domestic-abuse) and ``police mis-recording of abuse'', which is of direct interest to their data quality and reporting. 3. The programme on ``envionmental factors influencing abuse'' can be used to help predict which local populations are most at risk of abuse in the West Midlands,

@@

Within Lloyds Bank, we will work with Martin King, Head of Customer Vulnerability. Warwick already has a relation with King's team in CI Stewart's work on the effects of gambling, which was completed using micro-level transaction data from millions of account holders. Key issues here are work on coercion and control, and having sufficient financial resiliance to escape an abusive relationship and being able to make the decision to report an abuser. Our day-to-day contact at Lloyds is Dr David Leake, Head of the Behavioural Insights Team. We will present the findings from all four programmes to the Lloyds Vulnerability Team in six-monthly briefings, and work to integrate insight from the research into the Lloyds environment.

@@

Impact summit (1 day at the Shard) \TM{We haven't budgetted anything for this...}
Visits to key charities
Visits to West Midlands Police
Presentation to NPCC
Data sprint session with WMP Behavioural Insights Team?

@@

PI Mullett will spend half of his time of the project leading the impact activity and takes overall responsibility of delivering the impact programme. Mullett has worked extensively on the impact programme from the ESRC funded ``Accumulating to Choose'' programme, with the Financial Conduct Authority, and in his research on predicting alcohol related crime or health crises. CI Stewart will also spend half of his time of the project on the impact activity. Stewart has significant experience of impact acitivites in the domain of financial decision making with Lloyds Banking Group, Barclays Bank, and the UK Finance Association. Postdoc Trendl will be fully involved in the impact programme, and this is also an important part of the professional development for an early career researcher, and will allow her to establish a network of independent contacts. Trendl will spend one third of her time on the programme on the impact activities.
